---
title: "Multiple Linear Regression"
output:
  html_document:
    df_print: paged
---

# Overview


$Y = \beta_0 + \beta_1 x_1 + \beta_2 x_2 + \beta_3 x_3 + \beta_n x_n... + error$

``` {r, include=T}
library(readr)

expenses<-read_csv("C:/Users/Erick Gutierrez/Documents/GitHub/HW1-Group-5/expenses.csv",
    col_types = cols(
     age = col_double(),
     sex = col_factor(),
     bmi = col_double(),
     children = col_integer(),
     smoker = col_factor(),
     region = col_factor(),
     charges = col_double()
     ))
head(expenses)
```

# Exploratory Data Analysis

1. Checking distribution of target variable

```{r warning=F, message=F}
library(ggplot2)

ggplot(data=expenses, aes(expenses$charges))+
  geom_histogram(aes(y=..density..), fill="blue")+
  geom_density()

```


2. Analyzing Summary Statistics

```{r warning=FALSE, message=F}
library(psych)
psych::describe(expenses)

```

3. Checking Outliers Using Boxplots

```{r}

par(mfrow = c(2, 2))

boxplot(expenses$charges,
        main="Medical Charges",
        ylab="Dollars ($)",
        col="lightblue")

boxplot(expenses$bmi,
        main="Body Mass Index",
        ylab="Body Mass Index",
        col="lightblue")

boxplot(expenses$age,
        main="Individuals age",
        ylab="Years",
        col="lightblue")

boxplot(expenses$children,
        main="Number of Children",
        ylab="Children",
        col="lightblue")

par(mfrow = c(1, 1)) 
```

4. Correlation Matrix Visualization
```{r warning=F}
library(corrgram)
require(corrgram)
corrgram(expenses, order=TRUE, main="Correlation Matrix of Numeric Variables", diag.panel= panel.density, upper.panel=panel.cor, lower.panel=panel.fill)
mtext("Pearson's Correlation Coefficients", side=4, cex=1.2, line = -1.5, outer=T, xpd=NA)
```


# Training Regression Model

## Driving data into train and test subsets

```{r warning=F, message=F}
library(caret)
index<-createDataPartition(expenses$charges, p=0.7, list=F)
train<-expenses[index,]
test<-expenses[-index,]

dim(train)

```

## Building Model


```{r}

lmModel<-lm(charges~., data=train)
print(lmModel)

```

## Interpreting Regression Coefficients


## Validating Regression Coefficients and Models


```{r}
summary(lmModel)


```


1. Multiple R-squared:

2. Adjusted R-squared:

3. F-statistic:

4. AIC and BIC values:
```{r}
AIC(lmModel)
BIC(lmModel)
```
5. Root Mean Square Error:

```{r warning=FALSE, message=F}
library(Metrics)
rmse(actual = train$charges, predicted = lmModel$fitted.values)
```
